\section*{\centering Conferences}
\section*{International}
\begin{enumerate}
    \item \textbf{S. Divya} and T. Nann \enquote{Aluminum-Ion Batteries}, Pacific Climate Change Conference (\textbf{PCCC}), 2018, New Zealand.
    \item \textbf{S. Divya} and T. Nann- \enquote{New Cathodes for Aluminum-Ion Batteries.} 9th International Conference on Advanced Materials and Nanotechnology (\textbf{AMN9}), 2019, New Zealand.
    \item \textbf{S. Divya} and T. Nann- \enquote{Cathodes for Aluminum-Ion Batteries.} 10th International Conference on Materials for Advanced Technologies (\textbf{ICMAT}) by MRS Singapore, 2019, Singapore.
     \item \textbf{S. Divya} and T. Nann- \enquote{New Carbon Cathodes for Aluminum-Ion Batteries.} New Zealand Institute of Chemistry Conference (\textbf{NZIC}), 2019, New Zealand.
     \item \textbf{S. Divya}, J. Johnston and T. Nann- \enquote{New Cathodes for Rechargeable Aluminium-Ion Batteries.} TechConnect 2020, Washington D.C., USA, 2020. Abstract submitted.
\end{enumerate}
\section*{Domestic}   
\begin{enumerate}
     \item \textbf{S. Divya} and T. Nann- \enquote{New Cathodes for Aluminum-Ion Batteries.} Victoria University of Wellington-Massey University Symposium, 2018, New Zealand.
      \item \textbf{S. Divya} and T. Nann- \enquote{New Cathodes for Aluminum-Ion Batteries.} Nobel Prize Public Lecture at Victoria University of Wellington, 2019, New Zealand.
      \item \textbf{S. Divya}, J. Johnston and T. Nann- \enquote{Aluminum-Ion Batteries.}, Science Wairarapa, \textit{Invited talk}, May 2020, New Zealand.
\end{enumerate}

\section*{\centering Publications}
\begin{enumerate}
    \item \textbf{Shalini Divya}, James H.Johnston,and Thomas Nann.“Molybdenum Dichalcogenide Cathodes for Aluminium-Ion Batteries”. In: ArXiv191210607 Cond- MatPhysicsphysics (Dec. 2019) %\cite{divya_molybdenum_2019-1}
    \item \textbf{Shalini Divya} and Thomas Nann.“Carbon Cathodes for Rechargeable Aluminium-Ion Batteries”, to be submitted.
    \item \textbf{Shalini Divya}, Yuta Nakayasu,and Thomas Nann.“Molybdenum Dichalcogenide Nanoflowers as Cathodes for Non-Aqueous Aluminium-Ion Batteries”, to be submitted.
\end{enumerate}
\section*{\centering Patent}
